\documentclass[a4paper,10pt]{article}

\usepackage[left=0.7in, right=0.7in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}

% Blue color like image
\definecolor{headingblue}{RGB}{40, 70, 150}

% Section style
\titleformat{\section}
{\color{headingblue}\large\bfseries}
{}{}{ }[\titlerule]

\begin{document}

%-------------------- HEADER --------------------%
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}

{\LARGE \textbf{Ghanshyam }} & \\[4pt]

LinkedIn: \href{https://www.linkedin.com/in/ghanshyam-seervi-1b4b602a9}{\textcolor{blue}{ghanshyam-seervi}} 
& Email: Ghanshyamseervi1296@gmail.com \\

GitHub: \href{https://github.com/Ghan539}{\textcolor{blue}{Ghan539}} 
& Mobile: +91-7297979323 \\

\end{tabular*}

\vspace{-3pt}


%-------------------- SKILLS --------------------%
\section*{SKILLS}

\noindent
\textbf{Languages:} Python, SQL, Java (Basics) \\
\textbf{Libraries:} NumPy, Pandas \\
\textbf{Tools:} GitHub, VS Code, Streamlit, Jupyter Notebook \\
\textbf{Core Concepts:} OOPs, DBMS \\
\textbf{Soft Skills:} Analytical Thinking, Team Collaboration, Adaptability
%-------------------- PROJECTS --------------------%
\section*{PROJECTS}
\textbf{CertiCheck -- University Certificate Verification Platform} \hfill 2026\\[-4pt]
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]
\item Developed a platform to help universities verify the authenticity of student certificates submitted for internships, courses, and workshops.
\item Enabled faculty members to identify fake or tampered certificates before approval.
\item Used Python and OpenCV to analyze certificate features and validate documents.
\item Reduced manual verification time by providing a simple and centralized verification system.
\end{itemize}



\vspace{13pt}
%_______________________________________________
\noindent
\textbf{Linux world-Python mini project} \hfill 2025\\[-10pt]
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]
\item Built interactive dashboards using Streamlit.
\item Developed an AI-based chatbot application.
\item Implemented Text-to-Speech and Speech-to-Text systems.
\item Automated email workflows using Python.
\item Developed RESTful APIs using Flask.
\end{itemize}

%____________________________________________________________

\vspace{13pt}  % ✅ very light spacing (no overlap)

\noindent




%-------------------- TRAINING --------------------%
\section*{TRAINING}

\noindent
\textbf{Python Programming \& Automation Training – LinuxWorld Informatics Pvt. Ltd.} \hfill Nov 2025\\[-4pt]
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt]
\item Completed 40+ hours of hands-on training in Python programming and automation.
\item Gained practical experience in Flask web development, REST API development, and Streamlit dashboards.
\item Worked on automation tasks including email, SMS, and WhatsApp messaging systems.
\item Developed multiple real-world applications and improved problem-solving skills.
\end{itemize}
%-------------------- CERTIFICATIONS --------------------%
%-------------------- CERTIFICATIONS --------------------%
\section*{CERTIFICATIONS}

\noindent
\textbf{AWS Academy Graduate – Cloud Foundations}\hspace{6pt}
\href{https://www.credly.com/go/4JdUeFmv}{\textcolor{blue}{Link}}
\hfill Nov 2024\\[-8pt]

\noindent
\textbf{Generative AI: Elevate Your Data Science Career (IBM)} \hspace{6pt}
\href{https://coursera.org/verify/ZWJJGBDWDJJF}{\textcolor{blue}{Link}}
\hfill Feb 2025\\[-2pt]

%-------------------- EDUCATION --------------------%
\section*{EDUCATION}

\noindent
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}

\textbf{Vivekananda Global University, Jaipur} & 2024 -- 2028 \\
\hspace{2pt} B.Tech CSE (AI-DS), CGPA: 9.63 & \\[8pt]

\textbf{Wisdom Academy Senior Secondary School, Jodhpur} & 2022 -- 2023 \\
\hspace{2pt} 12th RBSE, Percentage: 83 & \\[8pt]

\textbf{Rani Devendra Kumari Public School, Jodhpur} & 2020 -- 2021 \\
\hspace{2pt} 10th CBSE, Percentage: 86 & \\

\end{tabular*}

\end{document}